Hispanic origin

### 2018-04-09 Code/7_Explore-Hispanic-origin.Rmd

fig3 <- ggplot(injuries, aes(x = Year, y = Age.Adjusted.Rate)) + geom_line(aes(col = Race, lty = Hispanic.Origin)) + facet_grid(State~Gender)
```

>>>>

fig3 <- ggplot(injuries, aes(x = Year, y = Age.Adjusted.Rate)) + geom_line(aes(col = Race, lty = Hispanic.Origin)) + facet_grid(State~Gender)

ggplot(injuries, aes(x = Year, y = Age.Adjusted.Rate)) + geom_point(aes(col = Race, shape = Hispanic.Origin)) + facet_grid(State~Gender)
```
